Hypertension and microbiome

### 2019-08-26 articletwo-sensitivityanalysis.Rmd
Fix model 1

```{r sensitivity analysis bp treat}
pseq.species.askbp <- subset_samples(pseq.species,
                                       PREVAL_DIAB == 0 &
                                       PREVAL_CHD == 0 &
                                       PREVAL_CR_ANYCANC == 0)

bray.dist.m.species.askbp <- bray.dist.m.species[pseq.species.askbp %>% meta %>% rownames,
                                                   pseq.species.askbp %>% meta %>% rownames]

alphadiversity.askbp <- calculate.alphadiversity(pseq.species.askbp,
                                                   list("max" = var.CL.opt,
                                                        "min" = var.CL.min))

betadiversity.askbp <- calculate.betadiversity(pseq = pseq.species.askbp,
                                                matrix = bray.dist.m.species.askbp,
                                                vars = list("max" = var.CL.opt,
                                                            "min" = var.CL.min))

>>>>

```{r sensitivity analysis bp treat}
alphadiversity.askbp <- calculate.alphadiversity(pseq.species,
                                                   list("max" = var.CL.opt,
                                                        "min" = var.CL.min))

betadiversity.askbp <- calculate.betadiversity(pseq = pseq.species,
                                                matrix = bray.dist.m.species,
                                                vars = list("max" = var.CL.opt,
                                                            "min" = var.CL.min))
